Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-25 src/tex/appendicies.tex
make plots prettier / less cluttery

\begin{eqnarray}
\tau_\lambda \propto \Gamma(a, b) \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
\end{eqnarray}

@@

\begin{align}
    \bm{p} \propto \mathcal{D}(m) \\
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_m)
\end{align}

\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
and $b_m$ is an array of $m$ different b shape parameters for the Gamma distribution.

>>>>

\begin{eqnarray}
\tau_\lambda \sim \Gamma(a, b) \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
\end{eqnarray}

@@

\begin{align}
    \bm{p} \sim \mathcal{D}(m) \\
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
\end{align}

\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
